---
output:
  pdf_document: default
  html_document: default
---
--
title: "ADBA_33333"
author: "Vikas"
date: "2024-02-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the relevant libraries
```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(rstan)
library(tidybayes)
library(modelr)
library(brms)
library(rstan)
library(bayesplot)
library(mcmcplots)
library(loo)
```

## Load the dataset and random sample
```{r, warning=FALSE, message=FALSE}

# Load dataset
#setwd("~/Documents")
booking_data1 <- read.csv("D:/Germany/Study Files-TUD/TU Dortmund/--------Semester-8-Winter Term--------2023-2024/Applied Bayesian Data Analysis/R/booking.csv", header = TRUE)

# Sample 10000 observations randomly
set.seed(123)
sampled_data <- booking_data1 %>%
sample_n(10000)

# Convert Cancellation Status, start by converting the categorical "booking.status" variable into numeric format:

sampled_data$cancellation_status <- ifelse(sampled_data$booking.status == "Canceled", 1, 0)
# unique(sampled_data$cancellation_status)
print(sampled_data$cancellation_status)
```

## Explore your dataset
```{r, warning=FALSE, message=FALSE}
head(sampled_data)
summary(sampled_data)
str(sampled_data)
```

## Setting up send & the priors and formulate the Bayesian Logistic Regression formula
```{r message=FALSE, warning=FALSE}

priors <- c(
  prior(normal(3.5, 1), class = "Intercept"),  # Adjusted mean and smaller scale
  prior(normal(0, 0.5), class = "b"),         # Smaller scale
  prior(normal(0, 0.5), class = "sd", coef = "sd")  # Smaller scale
)

lr_model <- brm(
  formula = booking.status ~
    number.of.adults + number.of.children + number.of.weekend.nights +
    number.of.week.nights + car.parking.space + lead.time + 
    P.C + P.not.C + average.price + special.requests + room.type, 
  data = sampled_data, 
  family = bernoulli("logit"),
  control = list(adapt_delta = 0.99, max_treedepth = 15),
)
```

## Summarizing the Bayesian Logistic Regression Model and plotting MCMC graphs
```{r, warning=FALSE, message=FALSE}
summary(lr_model)
mcmc_trace(lr_model)


# Saving summary plot
png("D:/Germany/Study Files-TUD/TU Dortmund/--------Semester-8-Winter Term--------2023-2024/Applied Bayesian Data Analysis/R/summary_plot_BayesianLogisticRegression.png", width = 800, height = 600, units = "px")
summary(lr_model)
dev.off()

# Saving trace plot
png("D:/Germany/Study Files-TUD/TU Dortmund/--------Semester-8-Winter Term--------2023-2024/Applied Bayesian Data Analysis/R/trace_plot_BayesianLogisticRegression.png", width = 800, height = 600, units = "px")
mcmc_trace(lr_model)
dev.off()
```

# Formulate the Binomial-Beta Model
```{r, warning=FALSE, message=FALSE}

binomial_beta_model <- brm(
  formula = cancellation_status | trials(10000) ~ number.of.adults + number.of.children + number.of.weekend.nights +
    number.of.week.nights + car.parking.space + lead.time + 
    P.C + P.not.C + average.price + special.requests + room.type,
  data = sampled_data,
  family = binomial(link = "logit"),
  prior = c(
    prior(normal(0, 10), class = "Intercept"),
    prior(normal(0, 1), class = "b")
  ),
  control = list(adapt_delta = 0.99, max_treedepth = 15),
  iter = 2000,
  warmup = 1000
)
```


## Summarizing the Binomial-Beta Model and plotting MCMC graphs
```{r, warning=FALSE, message=FALSE}

summary(binomial_beta_model)
mcmc_trace(binomial_beta_model)
plot(binomial_beta_model)



# Saving summary plot
png("D:/Germany/Study Files-TUD/TU Dortmund/--------Semester-8-Winter Term--------2023-2024/Applied Bayesian Data Analysis/R/summary_plot_Binomial-Beta.png", width = 800, height = 600, units = "px")
summary(binomial_beta_model)
dev.off()

# Saving trace plot
png("trace_plot_Binomial-Beta.png", width = 800, height = 600, units = "px")
mcmc_trace(binomial_beta_model)
dev.off()

# Saving plot
png("model_plot_Binomial-Beta.png", width = 800, height = 600, units = "px")
plot(binomial_beta_model)
dev.off()

```



## Model Comparison
```{r, warning=FALSE, message=FALSE}
# Compute LOO-CV for both models
loo_binomial <- loo(binomial_beta_model)
loo_logistic <- loo(lr_model)

# Compare the models using LOO-CV
loo_compare_result <- loo_compare(loo_binomial, loo_logistic)

# Print the comparison result
print(loo_compare_result)
```

## Model Comparison
```{r, warning=FALSE, message=FALSE}

library(bridgesampling)
(logml_lm1 <- bridge_sampler(lm1)) 
(logml_mlm2 <- bridge_sampler(mlm2))
```

